Compositional equivalences based on Open pNets

### 2020-09-04 2016-Weak-FH-Bisim/WeakBisim.tex
Some overfull hbox

We distinguish two kinds of parameterised actions: one that distinguishes input variables and one that does not. 
We first define the set of actions that distinguish input variables, they will be used in the definition of \pLTS\ below:
\[
\begin{array}[l]{rcl@{\quad}p{5.5cm}}
  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
  p_i&::=& ?x~|~e_i&\text{parameters (input variable or expression)}\\
  e_i&::=& \symb{Value}~|~x~|~\symb{op}(\symb{e}_1,..,\symb{e}_n)&\text{Expressions}
\end{array}
\]
The \emph{input variables} in an action term are those marked with a
$\symb{?}$.
We additionally suppose that each input variable does not
appear somewhere else in the same action term:
$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$.
We define $iv(t)$  as the set of input variables of a term $t$ (without the '?' marker).
Action algebras can encode naturally usual point-to-point message passing calculi (using 
$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
for more general synchronisation mechanisms, like gate negociation in Lotos, or broadcast
communications.

@@

A relation over the states of two open automata  $<\!J,\mathcal{S}_1, s_0,V_1,
   \mathcal{T}_1\!>$ and $<\!J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2\!>$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
$\mathcal{S}_2$ constrained by a predicate.
More precisely, for any pair $(s,t)\in \mathcal{S}_1\times \mathcal{S}_2$, there is a 
   single
      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
      if $\Pred_{s,t}$       is 
      True, i.e. the states are related when the variables in $V_1$ and $V_2$ verify the 
      predicate $\Pred_{s,t}$. By nature, this is well-defined if the variables of the two open automata are disjoint, i.e.  $V_1\cap V_2=\emptyset$.
 FH-bisimulation is defined formally: 
 \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim} ~\\
\noindent
\begin{minipage}{0.69\linewidth} 	Suppose 
   $A_1 = <\!J,\mathcal{S}_1, s_0,V_1,
   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2\!>$
   are open automata with identical holes of the same sort, with disjoint sets of variables.

@@

\item	The second rule deals with pNet nodes: for each possible
	synchronisation vector (of index $k$) applicable to the rule subject, the premisses
	include one {\em open transition} for each sub-pNet involved, one possible
	{\em action} for each hole involved, and the predicate relating these
	with the resulting action of the vector. The sub-pNets involved are split between two 
	sets, $I_2$ for sub-pNets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{({\alpha'})_m^{m 
	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
	I_2$}.                                                                    
\begin{mathpar}
    \mprset {vskip=.8ex}
\inferrule
    {
\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
\\
\\     	
	\forall m\!\!\in\!\! I_1. {\pNet_m 
	\models\openrule
    	{
    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\openrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {\alpha_m}
    		\ostate{s_m'}} }\\\\
    J' = \biguplus_{m\in I_1}\!\! J_m \uplus J	\\
    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
    \fresh(\alpha'_m,\alpha',\beta_j^{j\in J},\alpha) 
    }
    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\openrule
    		{
    		\beta_j^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }\quad {\TrDeux}
\end{mathpar} 
\end{itemize} 
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}
\end{definition}
        	A key to understand this rule is that the open transitions are
	expressed in terms of the leaves and holes of the whole pNet structure,
	i.e. a flatten view of the pNet. For example, $L$ is the index set of the
	Leaves, $L_m$ the index set of the leaves of one sub-pNet indexed $m$, so all $L_m$
	are disjoint subsets of $L$. Thus the states in the open transitions,
	at each level, are tuples including states of all the
	leaves of the pNet, not only those involved in the chosen
	synchronisation vector.

@@

We are now able to build a weak open automaton from an open automaton. This is done in a way that resembles the process of $\tau$ saturation: we add  $\tau$ open transitions before or after another (observable or not) open transition.
\begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
  Let $A = <J,\mathcal{S},s_0,V,\mathcal{T}>$ be an open automaton. 
The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,V,\WT>$ where $\WT$ is derived from $\mathcal{T}$ by saturation, applying the following rules.
%\noindent{\bf Invisible $\tau$ transitions:}
\begin{mathpar}
 \openrule
         {
           \emptyset,\symb{True},\Id(V)}
         {s \OTWeakarrow {\tau} s} \in \WT  \qquad \WTUn
 \end{mathpar}
and
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
} 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\qquad \WTDeux
%\inferrule{
% \openrule
%         {
%           \set{\beta},\Pred,\Post}
%         {s \OTarrow {\tau} s'} \in \mathcal{T}
%\\
% \openrule
%         {
%           \set{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
%         {s' \OTWeakarrow {\tau} s''} \in \WT
%}
%{ \openrule
%         {
%           \vis{\set{\beta}}\dotcup\set{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
%				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
%         {s \OTWeakarrow {\tau} s''} \in \WT
%}
 \end{mathpar}
 and
%\noindent{\bf Other transitions:}
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in \WT
\qquad
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
\qquad
\openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3  }
         {s_2 \OTWeakarrow {\tau} s'} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\shortotimes\Post_1}
\\
\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortotimes \Post_1}\\
\alpha'=\alpha\subst{\Post_1}
}
{
\openrule
         {\set{\gamma}
           ,
		\Pred,
				\Post_3\shortotimes\Post_2\shortotimes\Post_1} 
         {s \OTWeakarrow {\alpha'} s'} \in\WT
} \WTTrois
\end{mathpar}

@@

   \medskip     
The  \Post~of the weak OT $ WI_{6a}$ is:\\

$
\begin{array}{ll}
Post_{6a}&= post_{4}\shortotimes\ post_{456*}\shortotimes\ post_{6}\\ 
&=  (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})\,
\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+n) 
\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
&= (\texttt{m\_msg}\!\gets \texttt{s\_msg}, \texttt{m\_ec}\!\gets \texttt{s\_ec}+1\!+\!n, \texttt{s\_ec}\!\gets \texttt{s\_ec}+1\!+\!n)
\end{array}
$

@@

\subsection{Weak FH-bisimulation}
For defining a bisimulation relation between weak open automata, two options are possible. Either we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions. Or we define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transition of one open automaton with the transition of the weak open automaton derived from the second one.

@@

This already ensures the second part of the conclusion of the lemma, i.e. the OT for $Q$ 
if we 
choose  $\alpha_Q=\alpha_{j_0}$ and $\Pred\,''= \Pred_{j_0}$. 
Considering 
the OT of $P$ we have another  $J'$ that is $J'_p=J'\setminus\Holes(Q)\uplus 
\{j_0\}$; we denote $I'_1=I_1\setminus \{j_0\}$ the predicate is 
$\displaystyle{\Pred\,'=\!\!\!\!\!\bigwedge_{m\in I_1'\uplus I_2}\!\!\!\!\!\Pred_m  \land \Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in J\cup \{j_0\}},\alpha)}$
where\footnotemark[\thefootnote] $\Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in 
J\cup 
\{j_0\}},\alpha)\Leftrightarrow 
\forall i\in I'_1\uplus I_2.\, \alpha_i=\alpha'_i\land \forall j \in J\cup \{j_0\}.\, 
\beta_j=\alpha'_j 
\land 
\alpha=\alpha'
\land e_b$. Modulo renaming of fresh variables, this is identical to the predicate that 
occurs in 
the source open transition except $\alpha_{j_0}=\alpha'_{j_0}$ has been replaced by  
$\beta_{j_0}=\alpha'_{j_0}$. As $\alpha_{j_0}=\alpha_Q$ and $\beta_{j_0}$ is free, we 
have $\beta_{j_0}=\alpha'_{j_0}\land \beta_{j_0}=\alpha_Q \iff 
\alpha_{j_0}=\alpha'_{j_0}$.
Thus, $\Pred \iff (\Pred\,'
		\land \Pred\,'')\land \alpha_Q=\beta_{j_0}$. 
Finally, Post 
%conditions are easily split\footnote{\TODO{moved. could
%    even remove...?}Note that if the rules are not simplified, no
%  post-condition range over the variables of $P$ and $Q$ at the same
%  time} 
into conditions of the context $P$ and the pNet $Q$ (they are
builts similarly as they only deal with  
leaves): $\Post=\Post\,'\uplus \Post\,''$. This concludes the 
proof as we checked all the premises of the open transition for both $P$ and $Q$. We obtain the following reduction by the rule \TrDeux:
	\noindent
	\begin{small}
\begin{mathpar}
    \mprset {vskip=.8ex}
\inferrule
    {
\Leaves(\mylangle {\pNet}_m^{m\in I\setminus\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
\\
\\     	
	\forall m\!\!\in\!\! I_1\setminus\{j_0\}. {\pNet_m 
	\models\openrule
    	{
    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\openrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {\alpha_m}
    		\ostate{s_m'}} }\\\\
     J' = \biguplus_{m\in I_1 \setminus \{j_0\}}\!\! J_m \uplus J 	\\
    	\Pred\,' = \bigwedge_{m\in I_1\uplus I_2\setminus\{j_0\}}\!\! \Pred_m \land
    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2 \setminus \{j_0\}},\beta_j^{j\in J\cup\{j_0\}},\alpha)\\ 
    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1\setminus\{j_0\}}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
    }
    {\mylangle {\pNet}_m^{m\in I\setminus\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\openrule
    		{
    		{\beta_j}^{j\in J\setminus \Holes(Q)\uplus \{j_0\}}, \Pred\,',  \biguplus_{m\in I_1\setminus\{j_0\}\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
    			\ostate{(s_i^\prime)^{i\in L\setminus L_Q}}}
    	}
    }
\end{mathpar}
 \end{small}
\end{proof}

@@

>>>>

We distinguish two kinds of parameterised actions: one that distinguishes input variables and one that does not. 
We first define the set of actions that distinguish input variables, they will be used in the definition of \pLTS\ below:
\[
\begin{array}[l]{rcl@{\quad}p{7.5cm}}
  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
  p_i&::=& ?x~|~e_i&\text{parameters (input variable or expression)}\\
  e_i&::=& \symb{Value}~|~x~|~\symb{op}(\symb{e}_1,..,\symb{e}_n)&\text{Expressions}
\end{array}
\]
The \emph{input variables} in an action term are those marked with a
$\symb{?}$.
We additionally suppose that each input variable does not
appear somewhere else in the same action term:
$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$.
We define $iv(t)$  as the set of input variables of a term $t$ (without the '?' marker).
Action algebras can encode naturally usual point-to-point message passing calculi (using 
$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
for more general synchronisation mechanisms, like gate negociation in Lotos, or broadcast
communications.

@@

A relation over the states of two open automata  $<\!J,\mathcal{S}_1, s_0,V_1,
   \mathcal{T}_1\!>$ and $<\!J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2\!>$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
$\mathcal{S}_2$ constrained by a predicate.
More precisely, for any pair $(s,t)\in \mathcal{S}_1\times \mathcal{S}_2$, there is a 
   single
      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
      if $\Pred_{s,t}$       is 
      True, i.e. the states are related when the variables in $V_1$ and $V_2$ verify the 
      predicate $\Pred_{s,t}$. By nature, this is well-defined if the variables of the two open automata are disjoint, i.e.  $V_1\cap V_2=\emptyset$.
 FH-bisimulation is defined formally: 
 \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim} ~\\
\noindent
\begin{minipage}{0.67\linewidth} 	Suppose 
   $A_1 = <\!J,\mathcal{S}_1, s_0,V_1,
   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2\!>$
   are open automata with identical holes of the same sort, with disjoint sets of variables.

@@

\item	The second rule deals with pNet nodes: for each possible
	synchronisation vector (of index $k$) applicable to the rule subject, the premisses
	include one {\em open transition} for each sub-pNet involved, one possible
	{\em action} for each hole involved, and the predicate relating these
	with the resulting action of the vector. The sub-pNets involved are split between two 
	sets, $I_2$ for sub-pNets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{({\alpha'})_m^{m 
	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
	I_2$}.                                                                    
\begin{mathpar}
    \mprset {vskip=.8ex}
\inferrule
    {
\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \quad  	
k\!\in\! K \quad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
\\
\\     	
	\forall m\!\!\in\!\! I_1. {\pNet_m 
	\models\openrule
    	{
    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\openrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {\alpha_m}
    		\ostate{s_m'}} }\\\\
    J' = \biguplus_{m\in I_1}\!\! J_m \uplus J	\\
    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
    \fresh(\alpha'_m,\alpha',\beta_j^{j\in J},\alpha) 
    }
    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\openrule
    		{
    		\beta_j^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }\quad {\TrDeux}
\end{mathpar} 
\end{itemize} 
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}
\end{definition}
        	A key to understand this rule is that the open transitions are
	expressed in terms of the leaves and holes of the whole pNet structure,
	i.e. a flatten view of the pNet. For example, $L$ is the index set of the
	Leaves, $L_m$ the index set of the leaves of one sub-pNet indexed $m$, so all $L_m$
	are disjoint subsets of $L$. Thus the states in the open transitions,
	at each level, are tuples including states of all the
	leaves of the pNet, not only those involved in the chosen
	synchronisation vector.

@@

We are now able to build a weak open automaton from an open automaton. This is done in a way that resembles the process of $\tau$ saturation: we add  $\tau$ open transitions before or after another (observable or not) open transition.
\begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
  Let $A = <J,\mathcal{S},s_0,V,\mathcal{T}>$ be an open automaton. 
The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,V,\WT>$ where $\WT$ is derived from $\mathcal{T}$ by saturation, applying the following rules:
%\noindent{\bf Invisible $\tau$ transitions:}
\begin{mathpar}
 \openrule
         {
           \emptyset,\symb{True},\Id(V)}
         {s \OTWeakarrow {\tau} s} \in \WT  \qquad \WTUn
 \end{mathpar}
and
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
} 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\qquad \WTDeux
%\inferrule{
% \openrule
%         {
%           \set{\beta},\Pred,\Post}
%         {s \OTarrow {\tau} s'} \in \mathcal{T}
%\\
% \openrule
%         {
%           \set{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
%         {s' \OTWeakarrow {\tau} s''} \in \WT
%}
%{ \openrule
%         {
%           \vis{\set{\beta}}\dotcup\set{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
%				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
%         {s \OTWeakarrow {\tau} s''} \in \WT
%}
 \end{mathpar}
 and
%\noindent{\bf Other transitions:}
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in \WT
\qquad
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
\qquad
\openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3  }
         {s_2 \OTWeakarrow {\tau} s'} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\shortotimes\Post_1}
\\
\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortotimes \Post_1}\\
\alpha'=\alpha\subst{\Post_1}
}
{
\openrule
         {\set{\gamma}
           ,
		\Pred,
				\Post_3\shortotimes\Post_2\shortotimes\Post_1} 
         {s \OTWeakarrow {\alpha'} s'} \in\WT
} \WTTrois
\end{mathpar}

@@

   \medskip     
The  \Post~of the weak OT $ WI_{6a}$ is:

$$
\begin{array}{ll}
Post_{6a}&= post_{4}\shortotimes\ post_{456*}\shortotimes\ post_{6}\\ 
&=  (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})\,
\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+n) 
\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
&= (\texttt{m\_msg}\!\gets \texttt{s\_msg}, \texttt{m\_ec}\!\gets \texttt{s\_ec}+1\!+\!n, \texttt{s\_ec}\!\gets \texttt{s\_ec}+1\!+\!n)
\end{array}
$$

@@

\subsection{Weak FH-bisimulation}
For defining a bisimulation relation between weak open automata, two options are possible. Either we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions. Or we define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transition of the first one with the transition of the weak open automaton derived from the second one.

@@

This already ensures the second part of the conclusion of the lemma, i.e. the OT for $Q$ 
if we 
choose  $\alpha_Q=\alpha_{j_0}$ and $\Pred\,''= \Pred_{j_0}$. 
Considering 
the OT of $P$ we have another  $J'$ that is $J'_p=J'\setminus\Holes(Q)\uplus 
\{j_0\}$; we denote $I'_1=I_1\setminus \{j_0\}$ the predicate is 
$\displaystyle{\Pred\,'=\!\!\!\!\!\bigwedge_{m\in I_1'\uplus I_2}\!\!\!\!\!\Pred_m  \land \Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in J\cup \{j_0\}},\alpha)}$\\
where\footnotemark[\thefootnote] $\Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in 
J\cup 
\{j_0\}},\alpha)\Leftrightarrow 
\forall i\in I'_1\uplus I_2.\, \alpha_i=\alpha'_i\land \forall j \in J\cup \{j_0\}.\, 
\beta_j=\alpha'_j 
\land 
\alpha=\alpha'
\land e_b$. Modulo renaming of fresh variables, this is identical to the predicate that 
occurs in 
the source open transition except $\alpha_{j_0}=\alpha'_{j_0}$ has been replaced by  
$\beta_{j_0}=\alpha'_{j_0}$. As $\alpha_{j_0}=\alpha_Q$ and $\beta_{j_0}$ is free, we 
have $\beta_{j_0}=\alpha'_{j_0}\land \beta_{j_0}=\alpha_Q \iff 
\alpha_{j_0}=\alpha'_{j_0}$.
Thus, $\Pred \iff (\Pred\,'
		\land \Pred\,'')\land \alpha_Q=\beta_{j_0}$. 
Finally, Post 
%conditions are easily split\footnote{\TODO{moved. could
%    even remove...?}Note that if the rules are not simplified, no
%  post-condition range over the variables of $P$ and $Q$ at the same
%  time} 
into conditions of the context $P$ and the pNet $Q$ (they are
builts similarly as they only deal with  
leaves): $\Post=\Post\,'\uplus \Post\,''$. This concludes the 
proof as we checked all the premises of the open transition for both $P$ and $Q$. We obtain the following reduction by the rule \TrDeux:
	\noindent
	\begin{small}
\begin{mathpar}
    \mprset {vskip=.8ex}
\inferrule
    {
\Leaves(\mylangle {\pNet}_m^{m\in I\setminus\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
\\
\\     	
	\forall m\!\!\in\!\! I_1\setminus\{j_0\}. {\pNet_m 
	\models\openrule
    	{
    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\openrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {\alpha_m}
    		\ostate{s_m'}} }\\\\
     J' = \biguplus_{m\in I_1 \setminus \{j_0\}}\!\! J_m \uplus J 	\\
    	\Pred\,' = \bigwedge_{m\in I_1\uplus I_2\setminus\{j_0\}}\!\! \Pred_m \land
    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2 \setminus \{j_0\}},\beta_j^{j\in J\cup\{j_0\}},\alpha)\\ 
    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1\setminus\{j_0\}}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
    }
    {\mylangle {\pNet}_m^{m\in I\setminus\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\openrule
    		{
    		{\beta_j}^{j\in J\setminus \Holes(Q)\uplus \{j_0\}}, \Pred\,',  \biguplus_{m\in I_1\setminus\{j_0\}\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
    			\ostate{(s_i^\prime)^{i\in L\setminus L_Q}}}
    	}
    }
\end{mathpar}
 \end{small}
\end{proof}

@@

  \subsection{Test}

  $<1,2,3>$

  $\left< 1,2,3 \right>$
